---
title: "p8105_hw1_xw2757"
output: github_document
---
```{r}
library(tidyverse)
```

##Problem 1

**_Create a data frame comprised of:_**
 **_a random sample of size 10 from a standard Normal distribution_**
  **_a logical vector indicating whether elements of the sample are greater than 0_**
  **_a character vector of length 10_**
  **_a factor vector of length 10, with 3 different factor “levels”_**

```{r}
p1_df <- tibble(
  random_samp = rnorm(10),
  random_samp_pos = random_samp > 0,
  char_vec = c("This course", "is being offered", "in the Fall", "of 2021", "through the", "Biostatistics", "Department" , "at the",  "Columbia School", "of Public Health"),
  factor_vec = factor(c("dead", "alive", "zombie","dead","alive", "zombie","zombie", "zombie", "dead", "alive"))
)

view(p1_df)
```


**_Try to take the mean of each variable in your dataframe. What works and what doesn’t?_**

```{r}
mean(pull(p1_df, random_samp))
mean(pull(p1_df, random_samp_pos))
mean(pull(p1_df, char_vec))
mean(pull(p1_df, factor_vec))
```
mean of numeric vector and logical vector worked, but did not work for character and factor vectors.

**_In some cases, you can explicitly convert variables from one type to another. Write a code chunk that applies the as.numeric function to the logical, character, and factor variables (please show this chunk but not the output). What happens, and why? Does this help explain what happens when you try to take the mean?_**


```{r, eval=FALSE}
as.numeric(random_samp_pos)
as.numeric(factor_vec)
as.numeric(char_vec)
```
I can only convert the factor variable to numeric form. When I try to take the mean, factor variable and character variable would not compute because they are not numeric or logical. 



##Problem 2

**Use the code below to download the a package containing the penguins dataset:**
```{r, eval=FALSE}
install.packages("palmerpenguins")
```

**Next, use the following code (in your RMarkdown file) to load the penguins dataset:**

```{r}
data("penguins", package = "palmerpenguins")
```

**Write a short description of the penguins dataset (not the penguins_raw dataset) using inline R code, including:**
**the data in this dataset, including names / values of important variables**
**the size of the dataset (using nrow and ncol)**
**the mean flipper length**

 The size of the **penguins** dataset is `r nrow(penguins)` x `r ncol(penguins)`, with `r ncol(penguins)` variables and `r nrow(penguins)` observations.
 
 Variables described in this dataset are as followed: `r names(penguins)`.
 
```{r, echo=FALSE}
clean_penguins <- tidyr::drop_na(penguins, flipper_length_mm) 
```
 
 The mean of the sample's flipper length, given available data, is `r mean(pull(clean_penguins, flipper_length_mm))`.

**Make a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable (adding color = ... inside of aes in your ggplot code should help).**
**Export your first scatterplot to your project directory using ggsave.**

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = "red")) + geom_point()
ggsave("flipper_length_X_bill_length_Scatter.pdf", height=6, width= 6)
```









